Object-Oriented Internet - Azure Interoperability

### 2020-10-30 Latex/Manuscript.tex
Work out Markdown\20.Introduction.md #26
- final latex review
- fixes #26

\hypertarget{introduction}{%
      \section{Introduction}\label{introduction}}

@@

\begin{itemize}
      \tightlist
      \item
            \textbf{human-centric} - information origin or ultimate information
            destination is an operator,
      \item
            \textbf{machine-centric} - information creation, consumption,
            networking, and processing are achieved entirely without human
            interaction.
\end{itemize}

@@

From the M2M communication concept, a broader concept of a smart factory
can be derived. In this concept, the mentioned robots are only executive
assets of an integrated supervisory control system responsible for macro
optimization of an industrial process composed into one whole.
Deployment of the smart factory concept requires a hybrid solution and
interconnection of the mentioned above heterogeneous environments. This
approach is called the fourth industrial revolution and coined as
Industry 4.0. It is worth stressing that machines - or more general
assets - interconnection is not enough, and additionally, assets
interoperability has to be expected for the deployment of this concept.
In this case, multi-vendor integration makes communication
standardization especially important, namely it is required that the
payload of the message is standardized to be factored on the gathering
site and consumed on the ultimate destination site.

Highly-distributed solutions used to control real-time process
aggregating islands of automation (e.g.~virtual power plants producing
renewable energy) additionally must leverage public communication
infrastructure, namely the Internet. Internet is a demanding environment
for highly distributed process control applications designed atop the
M2M communication paradigm because

\begin{itemize}
      \tightlist
      \item
            it is a globally shareable environment and can be also used by
            malicious users
      \item
            it offers only non-deterministic communication making integration of
            islands of automation designed against the real-time requirements a
            difficult task
\end{itemize}

@@

\begin{itemize}
      \tightlist
      \item
            Human Machine Interface (HNI)
      \item
            Supervisory Control and Data Acquisition (SCADA)
      \item
            Distributed Control Systems (DCS)
\end{itemize}

@@

After dynamically attaching a new island of automation the control
application (responsible for the data pulling) must be reconfigured for
this interoperability scenario. In other words, in this case, the
interactive relationship cannot be directly applied because the control
application must be informed on how to pull data from a new source. As a
result, a plug and produce scenario cannot be seamlessly applied. A
similar drawback must be overcome if for security reasons suitable
protection methods have been applied to make network traffic propagation
asymmetric. It is accomplished using intermediary devices, for example,
firewalls, to enforce traffic selective availability based on
predetermined security rules against unauthorized access.

@@

If we must bother with the network traffic propagation asymmetry or
mobility of the asset network attachment-points the reactive
relationship could relax the problems encountered while the interactive
approach is applied. In this case, the sessionless publisher-subscriber
communication archetype is a typical pattern to implement the abstract
reactive interoperability paradigm. The sessionless archetype is a
message distribution scenario where senders of messages, called
publishers, do not send them directly to specific receivers, called
subscribers, but instead, categorize the published messages into topics
without knowledge about which subscribers if any, there may be.
Similarly, subscribers express interest in one or more topics and only
receive messages that are of interest, without knowledge about which
publishers, if any, there are. In this scenario, the publishers and
subscribers are loosely coupled.i.e they are decoupled in time, space
and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.

@@

Deployment of the hybrid solution providing interoperability of the
\textbf{machine-centric} CFSs and
\textbf{human-centric} cloud-based front-end can be implemented applying
the following scenarios:

\begin{itemize}
      \tightlist
      \item
            \textbf{direct interconnection} - cloud-based dedicated communication
            services allow to attache it to the CFS making up a
            consistent M2M communication network using an in-bound protocol stack
      \item
            \textbf{gateway based interconnection} - typical build-in
            communication services allows to attache the cloud computing to the
            CFS using an out-of-bound protocol stack
\end{itemize}

By design, the direct approach requires that the cloud has to be
compliant with the interoperability standard the CFS
is built around - it becomes a consistent part of the cyber-physical
system. Data models, roles, and responsibility differences of both
solutions make this approach impractical and imposable to be applied in
typical cases. A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.

@@

\begin{enumerate}
      \def\labelenumi{\arabic{enumi}.}
      \tightlist
      \item
            reactive interoperability M2M communication based on the OPC UA
            standard can be implemented as a powerful standalone library without
            dependency on the Client/Server session-oriented archetype
      \item
            Azure interoperability can be implemented as an external part
            employing out-of-band communication without dependency on the OPC UA
            implementation
      \item
            the proposed generic architecture allows that the gateway
            functionality is composable at run-time - no programming required
\end{enumerate}

The remainder of this paper is structured as follows. Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model. It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context. Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure. The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection. In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CFSs and cloud-based front-end. A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}. The most important findings and future work are summarized in Sect.~\ref*{architecture}.

\hypertarget{consider-to-add}{%
      \subsection{Consider to add}\label{consider-to-add}}

\hypertarget{scope}{%
      \subsubsection{Scope}\label{scope}}

What we must do to prove the goal have been achieved. Extent or range of
development, view, outlook, application, operation, effectiveness, etc.

\hypertarget{related-work}{%
      \subsubsection{Related work}\label{related-work}}

Any information about available reusable deliverables related to this work.

\hypertarget{cloud-to-sensors-field-level-connectivity}{%
      \section{Cloud to Sensors Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}}

\hypertarget{architecture}{%
      \subsection{Architecture}\label{architecture}}

@@

Using the session-oriented communication pattern it is difficult or
even impossible to gather and process mobile data (Sec. I), which is one
of the Internet of Things paradigms. OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit. As the result it can be recognized as the IoT ready technology.

@@

The following subsections covers description of the current state of technologies with regards to OPC UA pubsub and Azure cloud-based IoT enabler.

\hypertarget{azure-main-technology-features}{%
      \subsection{Azure Main Technology Features}\label{azure-main-technology-features}}

\hypertarget{services}{%
      \subsubsection{Services}\label{services}}

@@

\hypertarget{data-interchange}{%
      \subsubsection{Data Interchange}\label{data-interchange}}

@@

\hypertarget{connectivity}{%
      \subsubsection{Connectivity}\label{connectivity}}

@@

\hypertarget{ooi-main-technology-features}{%
      \subsection{OOI Main Technology Features}\label{ooi-main-technology-features}}

@@

\hypertarget{gateway-implementation}{%
      \section{Azure - Object-Oriented Internet interoperability Implementation}\label{gateway-implementation}}

@@

\hypertarget{conclusion}{%
      \section{Conclusion}\label{conclusion}}

>>>>

\section{Introduction}\label{introduction}

@@

\begin{itemize}
      \item \textbf{human-centric} - information origin or ultimate information destination is an operator,
      \item \textbf{machine-centric} - information creation, consumption, networking, and processing are achieved entirely without human interaction.
\end{itemize}

@@

From the M2M communication concept, a broader concept of a smart factory can be derived. In this concept, the mentioned robots are only executive assets of an integrated supervisory control system responsible for macro optimization of an industrial process composed into one whole. Deployment of the smart factory concept requires a hybrid solution and interconnection of the mentioned above heterogeneous environments. This approach is called the fourth industrial revolution and coined as Industry 4.0. It is worth stressing that machines - or more general assets - interconnection is not enough, and additionally, assets interoperability has to be expected for the deployment of this concept. In this case, multi-vendor integration makes communication standardization especially important, namely it is required that the payload of the message is standardized to be factored on the data  gathering site and consumed on the ultimate destination site.

Highly-distributed solutions used to control real-time process aggregating islands of automation (e.g.~virtual power plants producing renewable energy) additionally must leverage public communication infrastructure, namely the Internet. Internet is a demanding environment for highly distributed process control applications designed atop the M2M communication paradigm because
\begin{itemize}
      \item it is a globally shareable environment and can be also used by malicious users
      \item it offers only non-deterministic communication making integration of islands of automation designed against the real-time requirements a difficult task
\end{itemize}

@@

\begin{itemize}
      \item  Human Machine Interface (HNI)
      \item Supervisory Control and Data Acquisition (SCADA)
      \item Distributed Control Systems (DCS)
\end{itemize}

@@

After dynamically attaching a new island of automation the control application (responsible for the data pulling) must be reconfigured for this interoperability scenario. In other words, in this case, the interactive communication relationship cannot be directly applied because the control application must be informed on how to pull data from a new source. As a result, a plug and produce scenario cannot be seamlessly applied. A similar drawback must be overcome if for security reasons suitable protection methods have been applied to make network traffic propagation asymmetric. It is accomplished using intermediary devices, for example, firewalls, to enforce traffic selective availability based on predetermined security rules against unauthorized access.

@@

If we must bother with the network traffic propagation asymmetry or mobility of the asset network attachment-points the reactive relationship could relax the problems encountered while the interactive approach is applied. In this case, the sessionless publisher-subscriber communication relationship is a typical pattern to implement the abstract reactive interoperability paradigm. The sessionless relationship is a message distribution scenario where senders of messages, called publishers, do not send them directly to specific receivers, called subscribers, but instead, categorize the published messages into topics without knowledge about which subscribers if any, there may be. Similarly, subscribers express interest in one or more topics and only receive messages that are of interest, without knowledge about which publishers, if any, there are. In this scenario, the publishers and subscribers are loosely coupled.i.e they are decoupled in time, space and synchronization \cite{RefWorks:doc:5c44e246e4b0591b15ea9e59}.

@@

Deployment of the hybrid solution providing interoperability of the \textbf{machine-centric} cyber-physical system (CFS) and \textbf{human-centric} cloud-based front-end can be implemented applying the following scenarios:

\begin{itemize}
      \item \textbf{direct interconnection} - cloud-based dedicated communication services allow to attache it to the CFS making up a consistent M2M communication network using an in-bound protocol stack
      \item \textbf{gateway based interconnection} - typical build-in communication services allows to attache the cloud computing to the CFS using an out-of-bound protocol stack
\end{itemize}

By design, the direct approach requires that the cloud has to be compliant with the interoperability standard the CFS is built upon - it becomes a consistent part of the CFS. Data models, roles, and responsibility differences of both solutions make this approach impractical or even imposable to be applied in typical cases. A more detailed description is covered by the Sect.~\ref*{cloud-to-sensors-field-level-connectivity}.

@@

\begin{enumerate}
      \item  reactive interoperability M2M communication based on the OPC UA standard can be implemented as a powerful standalone library without dependency on the Client/Server session-oriented archetype
      \item Azure interoperability can be implemented as an external part employing out-of-band communication without dependency on the OPC UA implementation
      \item the proposed generic architecture allows that the gateway functionality is implemented as composable part at run-time part - no programming required
\end{enumerate}

The remainder of this paper is structured as follows. Sect.~\ref*{cloud-to-sensors-field-level-connectivity} presents the proposed open and reusable software model. It promotes a reactive interoperability pattern and a generic approach to establishing interoperability-context. A reference implementation of this archetype is described in Sect.~\ref*{gateway-implementation}. The most important findings and future work are summarized in Sect.~\ref*{conclusion}.

\section{Cloud to Sensors Field Level Connectivity}\label{cloud-to-sensors-field-level-connectivity}

\subsection{Architecture}\label{architecture}

@@

Using the session-oriented communication pattern it is difficult or even impossible to gather and process mobile data (Sec.~\ref*{introduction} ), which is one of the Internet of Things paradigms. OPC UA Part 14 PubSub \cite{RefWorks:doc:5d98837de4b055984c0eecf0} \todo{add ref: Mariusz Postol, UA Part 14: PubSub Main Technology Features in Object Oriented Internet, https://github.com/mpostol/OPC-UA-OOI, 2019, DOI: 10.5281/zenodo.1198852} offers the sessionless approach as an additional option to session based client-server interoperability relationship and is a consistent part of the OPC UA specifications suit. As the result it can be recognized as the IoT ready technology.

@@

The following subsections cover the description of the current state of technologies with regards to Azure cloud-based IoT enabler and OPC UA pubsub. Sect.~\ref*{azure-main-technology-features} analyzes data presentation user interface, available native communication services, and data/metadata model offered by the Microsoft Azure. The discussion covered by this section is the foundation for selecting services utilized to expose process data and suitable protocol stack to support interconnection. In Sect.~\ref*{ooi-main-technology-features} the discussion focuses on the generic architecture that is to be used as a foundation for further decisions addressing the systematic design of the interoperability of the CFSs and cloud-based front-end.

\subsection{Azure Main Technology Features}\label{azure-main-technology-features}

\subsubsection{Services}\label{services}

@@

\subsubsection{Data Interchange}\label{data-interchange}

@@

\subsubsection{Connectivity}\label{connectivity}

@@

\subsection{OOI Main Technology Features}\label{ooi-main-technology-features}

@@

\section{Azure - Object-Oriented Internet interoperability Implementation}\label{gateway-implementation}

\todo{Add any information about available reusable deliverables related to this work.}

@@

\section{Conclusion}\label{conclusion}
